Regime transition identification for basin's governance challenges of water use

### 2020-11-20 tex/main/manuscript.tex
change fig.4 and related descriptions

\begin{figure}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
	\caption{
		Causes of water governance regime shifts: environment changes, economic growths and efficiency changes, social transformation and water governance policies.
		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Appendix} Method S2).
		\textbf{C.} Completed time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time. Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage. These marked reservoirs, therefore are significant for the entire basin, far crucial than regional development.
	}
	\label{fig:Causes}
\end{figure}

@@

% 不断变化的管理模式。
Finally, environmental context, social transformation and water governance policies played roles throughout all three periods. 
According to the location, we calculate the ratios of regional and basinal water use for each reservoir.
In the P1 when natural water resource is relatively abundant (see \textit{SI Appendix} Figure S3), most of the reservoirs are built in regions with high water demands, as ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01). 
In the P2, the number of new reservoirs decreases significantly with little increment of total storage capacities (\textit{SI Appendix} Fig. S6).  
Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig. S6).
% After the major environmental regulation, myriad new water policies proposed during this period.

>>>>

\begin{figure}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
	\caption{
		Causes of water governance regime shifts: environment changes, economic growths and efficiency changes, social transformation and water governance policies.
		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Appendix} Method S2).
		\textbf{C.} Completed time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time. Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage. These marked reservoirs, therefore are significant for the entire basin, far crucial than regional development.
		\textbf{D.} Social transformations and national levels' policies related to water governance (see \textit{Appendix SI} Table S2). Four transformations are ``ethos of overcome nature since 1958'', ``reform and opening-up since 1978'', ``the 87 Water Diversion Scheme since 1987'', ``environmental regulation since 2003'' in order.
	}
	\label{fig:Causes}
\end{figure}

@@

% 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
Finally, environmental context, social transformation and water governance policies played roles throughout all three periods. 
% 根据水库的位置，计算了各水库的区域用水量与盆地用水量之比。
According to locations, we calculate the ratios of regional and basinal water use for each reservoir (R/B ratio), and a higher ratio represents potential role for storage rather than regulating (see \textit{SI Appendix} Figure S3).
% 在自然水资源相对丰富的P1年，水库大多建在需水量高的地区，水库的需水量比显著偏高。
Under the guide of ``ethos of overcome nature'', most of the reservoirs are built in regions with high water demands during the P1, when natural water resource is relatively abundant, as R/B ratios are significantly higher (Figure~\ref{fig:Causes}C, p<0.01). 
% 在P2中，新水库的数量显著减少，水量分配受到“87调水方案”的严格控制，总库容几乎没有增加(\textit{SI  Appendix}图S6)。
In the P2, the number of new reservoirs decreases significantly and allocation of water were rigorously controlled by ``the 87 Water Diversion Scheme'', with little increment of total storage capacities (\textit{SI Appendix} Fig. S6). 
% 而进入P3期后，新增水库数量远高于P1期，且多数建在区域用水量比较低的区域(图~\ref{fig: Causes}C和\textit{SI  Appendix}图S6)。
Entering the P3, myriad national-level water governance policies proposed under the guide of ``environmental regulation'', and the number of new reservoirs are even higher for facilitating regulation, most of which were built in regions with lower R/B ratio (Figure~\ref{fig:Causes}C and \textit{SI Appendix} Fig. S6).
